\documentclass[a4paper,11pt]{article}
\usepackage{a4wide,graphicx,amsmath,amssymb,amsthm, algpseudocode, algorithm}
\usepackage[ruled, noline, algo2e, noend]{algorithm2e}
%\usepackage{hyperref,url,color}
%\urlstyle{rm}

%----------------------- Macros and Definitions --------------------------

\newcommand{\N}{\ensuremath{\mathbb{N}}}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\Z}{\ensuremath{\mathbb{Z}}}
\newcommand{\M}{\ensuremath{\mathcal{M}}}

\graphicspath{{./images/}}

%-------------------------------- Title ----------------------------------

\title{Report Autonomous Vehicles and AI\\[1ex]
%
\large Autonomous Vehicles and Artificial Intelligence Lab}

\author{
    K. L. \\
    \and
    N. O. \\
    \and
    J. D. \\
    \and
    A. A.
}
\date{\today}

%--------------------------------- Text ----------------------------------

\begin{document}
\maketitle

\section{Introduction}

The F1Tenth car platform is a project for a small model race car and implements basic functionality like driving and steering. 
It also already comes with all the nodes required to fetch and publish sensor and transform data.

The developers provide manuals to build the hardware of the car platform and a software stack to interact with the basic components like steering, acceleration and the sensors. All of this is already implemented by the university staff and the interface is documented on the Github Repository of the F110 team.
In order to make it available in Gazebo Fortress I needed to implement an SDF file that implements the F110 standard in order for the simulation to be as close as possible to the real-world car platform.
The F110 car platform comes a 4-wheel drive, steering, IMU sensor, depth camera, RGB-camera and a LiDAR sensor.

\section{Expectations}

% Here we could list our requirements and compare what we actually wanted achieved
The goal of this project is to develop an autonomous race car capable of completing at least one lap on an indoor track in a fast yet safe manner. The vehicle is positioned in the driving direction at the start. The race environment follows the F1TENTH cone system, where blue cones mark the left boundary, yellow cones mark the right boundary, and the start zone is identified by orange cones on both sides. The track is a closed-loop circuit without any branches, and its layout changes between races. The vehicle operates without other cars on the track, with a maximum speed of approximately 15 km/h. A perception round precedes the timed lap. The system utilizes ROS for software integration and runs on an NVIDIA Jetson NX 16GB. The vehicle is equipped with a 3D + mono camera (Intel RealSense Depth Camera D435i) and a high-resolution 2D LiDAR (Hokuyo UST-10), and it features a four-wheel-drive system with Ackermann steering for navigation.

\section{Architecture}


\section{Simulation}

\include{simulation}

\section{Challenges}

\section{Tests}

% Here we could come back to the expectations and discuss why we did not do some parts

\bibliographystyle{alpha}
\bibliography{bibliography}

\end{document}
